%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Joseph Ellis} % Your name
%\address{5526 South Everett Ave} % Your address
%\address{Chicago, IL 60637} % Your address
\address{ellis125@gmail.com} % Your phone number and email
\address{www.ellisjoe.com}
\address{(815) 388-2890}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Chicago} \hfill {\em June 2015} \\ 
B.S. and M.S. in Computer Science \\
Member of the Varsity Wrestling Team \\

\vspace{-1em}

\begin{rSubsection}{Master's Research Project}{June 2014 - June 2015}{UCARE Research Team}{Chicago, IL}
\item Researched Hadoop's ability to handle degraded networks while using erasure encoded storage.
\item Proposed a new method of handling degraded networks when using erasure encoded storage.
\item Created analytic models and ran test workloads on Hadoop to analyze performance.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Palantir Technologies}{June 2015 - Present}{Software Engineer}{Palo Alto, CA}
\item Work with the distributed computation and data integration teams.
\item Design and implement new features allowing for the analysis of petabytes of data.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Palantir Technologies}{June 2014 - September 2014}{Software Engineer Intern}{Palo Alto, CA}
\item Added the ability to export data from the distributed compute engine to databases such as Elasticsearch.
\item Designed and built a web application that allows users to remotely configure their servers.
\item Worked with team members to design and build deployment management software.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Palantir Technologies}{June 2013 - September 2013}{Infrastructure Quality Engineer Intern}{Palo Alto, CA}
\item Automate existing tests and contribute new functionality to the automation framework
\item Design and execute tests related to functionality and scalability.
\item Debug software and server issues.
\item Find and file defects and verify fixed deficiencies.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{University of Chicago}{June 2012 - June 2014}{Teaching Assistant}{Chicago, IL}
\item Built a system allowing student work to be analyzed for plagiarism.
\item Graded student coursework.
\item Helped students during weekly lab exercises.
\item Answered questions using an online forum.
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL INTERESTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills and Interests}

\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
\itemsep -0.5em % \vspace{-0.5em} % Compress items in list together for aesthetics
\item Proficient in Java, C, C++, Python, SQL, and Bash.
\item Experience with web development including Javascript, HTML, and CSS.
\item Experience with systems including Hadoop, Spark, PostgreSQL, MySQL, and Elasticsearch.
\item Interested in the design and implementation of distributed systems.
\end{list}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
